Next Trippy Structures\thanks{Supported by organization x.}

### 2018-12-20 paper.tex
State of the art!

\section{State of the Art}
Review whatever we may have missed from state of the art in prev. papers. Also explain ZSTD and applications. Finally, explain our work-in-progress model for trip representation.

@@

\begin{theorem}
This is a sample theorem. The run-in heading is set in bold, while
the following text appears in italics. Definitions, lemmas,
propositions, and corollaries are styled the same way.
\end{theorem}
%
% the environments 'definition', 'lemma', 'proposition', 'corollary',
% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%
\begin{proof}
Proofs, examples, and remarks have the initial word in italics,
while the following text appears in normal font.
\end{proof}
For citations of references, we prefer the use of square brackets
and consecutive numbers. Citations using labels or the author/year
convention are also acceptable. The following bibliography provides
a sample reference list with entries for journal
articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
and a homepage~\cite{ref_url1}. Multiple citations are grouped
\cite{ref_article1,ref_lncs1,ref_book1},
\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}
\bibitem{ref_article1}
Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)

\bibitem{ref_lncs1}
Author, F., Author, S.: Title of a proceedings paper. In: Editor,
F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
Springer, Heidelberg (2016). \doi{10.10007/1234567890}

\bibitem{ref_book1}
Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
Location (1999)

\bibitem{ref_proc1}
Author, A.-B.: Contribution title. In: 9th International Proceedings
on Proceedings, pp. 1--2. Publisher, Location (2010)

\bibitem{ref_url1}
LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
Oct 2017
\end{thebibliography}
\end{document}

>>>>

\section{State of the Art}
A nice review of all the R-Tree derivatives: \cite{john2017performance}.

Review whatever we may have missed from state of the art in prev. papers \cite{koide2018cinct} and \cite{ding2018ultraman}. For vehicles we also have this \cite{cai2018vector} and \cite{lovell2018lossless}. On contrast, in \cite{al2017semantictraj} we have a very nice example of a text-based trajectory indexing. I need to figure out what the Geodabs thing \cite{chapuis2018geodabs} is all about.

Cite Adrian and all that crap.

Cite ways of obtaining the data we need, to show that it's possible even though we couldn't get any. You can get a lot of info from smart cards \cite{bhaskar2015passenger}, smart cards + gps \cite{ma2014development}, and even cellphone data \cite{liu2017exploring}. These guys also focus on trajectory reconstruction \cite{tao2014exploring}. These guys \cite{wang2014aggregated} made it so boring that they are probably not worth citing. To the ones who wonder how do we know the final stops, they figured it out in \cite{alsger2016validating}.

If possible, cite applications of our kind of analysis for transportat/ad companies, to show that what we are doing is useful. One example is \cite{tu2018spatial}. Another is \cite{zhang2017targeted}. And by the way, the guys in \cite{weng2018mining} do some analysis with data that has already boarding and alighting stops!

Explain ZSTD and applications.

Finally, explain our work-in-progress model for trip representation, citing SPIRE. Newer models are largely irrelevant.

@@

\begin{theorem}
This is a sample theorem. The run-in heading is set in bold, while
the following text appears in italics. Definitions, lemmas,
propositions, and corollaries are styled the same way.
\end{theorem}
%
% the environments 'definition', 'lemma', 'proposition', 'corollary',
% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%
\begin{proof}
Proofs, examples, and remarks have the initial word in italics,
while the following text appears in normal font.
\end{proof}

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.

\bibliographystyle{splncs04}
\bibliography{refs}

\end{document}
